---
title: "10-import"
output: html_notebook
---


1. Describe the data and the problem

**Hapiness is important because it's extremely vital to out own goals in life and can help us achieve many other cherished personal ambitions and goals. Also, by being happy, we have the potantial to change many other lives just by being ourselves. I went to hiking trip last week and we talked about the measurements in happiness on our way back home. Some people say people who'd rather die at their 80s are happier than those who want to die at their 40s (life expentancy) and some people have other paramters for happiness. I think it might be interesting and meaningful to dive into some data to dig out what really matters towards happiness. In this project, I use the data from The World Happiness Report, a landmark survey of the state of global happiness. The World Happiness 2017, which ranks 155 countries by their happiness levels, was released at the United Nations at an event celebrating International Day of Happiness on March 20th. Leading experts across fields – economics, psychology, survey analysis, national statistics, health, public policy and more – describe how measurements of well-being can be used effectively to assess the progress of nations.**

The dataset that I chosen is happiness 2016-2017 dataset, one of Kaggle’s dataset. This dataset gives the happiness rank and happiness score of 155 countries around the world based on seven factors including family, life expectancy, economy, generosity, trust in government, freedom, and dystopia residual. Sum of the value of these seven factors gives us the happiness score and the higher the happiness score, the lower the happiness rank. So, it is evident that the higher value of each of these seven factors means the level of happiness is higher. We can define the meaning of these factors as the extent to which these factors lead to happiness. Dystopia is the opposite of utopia and has the lowest happiness level. Dystopia will be considered as a reference for other countries to show how far they are from being the poorest country regarding happiness level.


The purpose of choosing this work is to find out which factors are more important to live a happier life. As a result, people and countries can focus on the more significant factors to achieve a higher happiness level. We also will implement several machine learning algorithms to predict the happiness score and compare the result to discover which algorithm works better for this specific dataset.


```{r libraries}
library(readr)
library(tidyverse)
library(janitor)
library(assertr)
```


```{r read data and clean names}
happy2016 <- read_csv("data/2016.csv") %>%
  clean_names() 
happy2017 <- read_csv("data/2017.csv")%>%
  clean_names() 
```

```{r check the structure}
str(happy2016)
str(happy2017)
```



```{r select colomn I interested and combine them together} 
use2016 <- happy2016[c(1,3,7,8,9,10,11,12,13)]
use2017 <- happy2017[c(1,2,6,7,8,9,10,11,12)]

df<- merge(use2016, use2017,
           by.x = "country",
           by.y = "country")
```

```{r get the colomn name}
colnames(df)
```

```{r testing happiness rank}
df %>% 
 verify(happiness_rank.x>0) %>% 
 verify(happiness_rank.y>0)
```

```{r tesing hapiness rank}
df %>% 
  assert(within_bounds(1,157),happiness_rank.x) %>% 
  assert(within_bounds(1,157),happiness_rank.y)
```


```{r get rid of NAs}
df1 <- na.omit(df)
```


**Definitions of each parameters

**Country**: Name of the country.

**Region**: Region the country belongs to.

**Happiness Rank**: Rank of the country based on the Happiness Score.

**Happiness Score**: A metric measured in 2016 and 2017 by asking the sampled people the question: "How would you rate your happiness on a scale of 0 to 10 where 10 is the happiest."

**Economy (GDP per Capita)**: The extent to which GDP contributes to the calculation of the Happiness Score.

**Family**: The extent to which Family contributes to the calculation of the Happiness Score.

**Health (Life Expectancy)**: The extent to which Life expectancy contributed to the calculation of the Happiness Score

**Freedom**: The extent to which Freedom contributed to the calculation of the Happiness Score.

**Trust (Government Corruption)**: The extent to which Perception of Corruption contributes to Happiness Score.

**Generosity**: Generosity is a quality that's a lot like unselfishness. Someone showing generosity is happy to give time, money, food, or kindness to people in need.

**Dystopia Residual**: Dystopia is an imaginary country that has the world’s least happy people, while residuals refer to the unexplained components that contribute to a country’s happiness.