---
title: "30-feature-engineering"
output: html_notebook
---



# Midterm Second Half Arsalan Riaz

Find the difference in health scores between 2016 and 2017.

The function performs subtraction and adds a new column 'Health_Score_Diff' to the dataset df1.

health life ecpectancy is one of the main factors in calculating the happiness score and rank. The higher the score the lesser the rank. In this function we are taking the difference between health life expectancy in 2017 and health life expectancy in 2016. The difference will show whether it is an overall rise or fall in the health life expectancy from 2016 to 2017. Positive values will denote a betterment and negative will denote a fall.

Assert staement to confirm that the value never breaches -1 and 1.

The scipen command is used to turn the differnce values received as a power of e into decimals


```{r calculating the difference between health life expectancy in 2016 and 2017}

options(scipen = 50)
Health_Difference <- function(df,x,y) {
  
  df %>% 
    mutate(Health_Difference = {{y}} - {{x}})
}


df1 %>% 
Health_Difference(health_life_expectancy.x, health_life_expectancy.y ) %>% 
  select(Health_Difference, everything()) %>% 
  arrange(-Health_Difference) %>% 
  assert(within_bounds(-1,1),Health_Difference)

```


# Problem 2: This is simply an addition function on three variables

You should combine these parameters towards social satisfaction, which including economy_gdp_per_capita.x, trust_government_corruption.x, dystopia_residual.x.

.x denotes the values of 2016

In order to know the social satisfaction score i.e. social satis from the data we wil need to add economy_gdp_per_capita.x(The extent to which GDP contributes to the calculation of the Happiness Score), trust_government_corruption.x (The extent to which Perception of Corruption contributes to Happiness Score) and dystopia_residual.x (Dystopia is an imaginary country that has the world’s least happy people, while residuals refer to the unexplained components that contribute to a country’s happiness). All of these scores add up to determine the social satisfaction score and play an integeral part in determining the happiness score and rank as well.
The assert statements to show the values lie within the maximum and minimum bounds of the data i.e. 0 and 5



```{r adding economy_gdp_per_capita.x, trust_government_corruption.x and dystopia_residual.x to determine Social Satisfaction Score }

get_social_satis <-  function(df,x,y,z) {
  
  df %>% 
    mutate(social_satis = {{x}} + {{y}} + {{z}})
  
  
}


df1 %>% 
  get_social_satis(economy_gdp_per_capita.x, trust_government_corruption.x, dystopia_residual.x) %>% 
  select(social_satis, everything()) %>% 
  arrange(-social_satis) %>% 
  assert(within_bounds(0,5), social_satis)


```




Right now, we want to calculate the differnce of each parameters. This can help us to see if the changes in rating matches the changes of each countries' happiness score. 

```{r difference in happiness rank}
Happiness_Rank_Difference<- function(df, y,x){
  df %>% 
  mutate(Happiness_Rank_Difference= {{y}}-{{x}}) 
}
```


Test and assert the differnt funciton.
```{r test Happiness_Rank_Difference function}
Happiness_Rank_Difference(df1,happiness_rank.y, happiness_rank.x) %>% 
  select(happiness_rank.y, happiness_rank.x,Happiness_Rank_Difference) %>% 
  assert(within_bounds(lower.bound = -Inf, upper.bound = Inf, allow.na = FALSE), Happiness_Rank_Difference)
```


Create function of difference in Economics
```{r}
Economics_Difference <-function(df,y,x){
  df %>% 
  mutate(Economics_Difference= {{y}}-{{x}}) 
}
```

```{r test Economics_Difference function}
Economics_Difference(df1, economy_gdp_per_capita.y, economy_gdp_per_capita.x) %>% 
  select(economy_gdp_per_capita.y, economy_gdp_per_capita.x, Economics_Difference) %>% 
  assert(within_bounds(lower.bound = -Inf, upper.bound = Inf, allow.na = FALSE), Economics_Difference)
```


Create function of difference in Family.

```{r}
Family_Difference <- function(df,y,x){
    df %>% 
    mutate(Family_Difference= {{y}}-{{x}})
}
```


```{r test Family_Difference function}
Family_Difference(df1,family.y,family.x) %>% 
  select(family.y,family.x,Family_Difference) %>% 
  assert(within_bounds(lower.bound = -Inf, upper.bound = Inf, allow.na = FALSE), Family_Difference)
```

Create function of difference in Health.
```{r}
#Health_Difference
```



```{r test Health_Difference function}
Health_Difference(df1,health_life_expectancy.y,health_life_expectancy.x) %>% 
  select(health_life_expectancy.y,health_life_expectancy.x, Health_Difference) %>% 
  assert(within_bounds(lower.bound = -Inf, upper.bound = Inf, allow.na = FALSE), Health_Difference)
```


In the original dataset, we have one colomn called region. I want to create a new feature of continents to better group those countries. 

```{r get continent function}
get_continent <- function(df, x){
  
  return_continent <- function(country){ 
  Europe <- c("Norway", "Denmark", "Iceland", "Switzerland", "Finland","Netherlands", "Sweden", "Austria", "Ireland", "Germany","Belgium", "Luxembourg", "United Kingdom", "Czech Republic","Malta", "France", "Spain", "Slovakia", "Poland", "Italy","Russia", "Lithuania", "Latvia", "Moldova", "Romania","Slovenia", "North Cyprus", "Cyprus", "Estonia", "Belarus","Serbia", "Hungary", "Croatia", "Kosovo", "Montenegro","Greece", "Portugal", "Bosnia and Herzegovina", "Macedonia","Bulgaria", "Albania", "Ukraine")
  Australia <- c("New Zealand", "Australia")
  Asia <- c("Israel", "United Arab Emirates", "Singapore", "Thailand", "Taiwan Province of China","Qatar", "Saudi Arabia", "Kuwait", "Bahrain", "Malaysia", "Uzbekistan", "Japan","South Korea", "Turkmenistan", "Kazakhstan", "Turkey", "Hong Kong S.A.R., China", "Philippines","Jordan", "China", "Pakistan", "Indonesia", "Azerbaijan", "Lebanon", "Vietnam","Tajikistan", "Bhutan", "Kyrgyzstan", "Nepal", "Mongolia", "Palestinian Territories","Iran", "Bangladesh", "Myanmar", "Iraq", "Sri Lanka", "Armenia", "India", "Georgia", "Cambodia", "Afghanistan", "Yemen", "Syria")
  North_America <- c("Canada", "Costa Rica", "United States", "Mexico",  
"Panama","Trinidad and Tobago", "El Salvador", "Belize", "Guatemala","Jamaica", "Nicaragua", "Dominican Republic", "Honduras","Haiti")
  South_America <- c("Chile", "Brazil", "Argentina", "Uruguay","Colombia", "Ecuador", "Bolivia", "Peru","Paraguay", "Venezuela")
  Africa <- c("Algeria","Angola","Benin","Botswana","Burkina Faso","Burundi","Cameroon","Chad","Congo (Brazzaville)","Congo (Kinshasa)","Egypt","Ethiopia","Gabon","Ghana","Guinea","Ivory Coast","Kenya","Liberia","Libya","Madagascar","Malawi","Mali","Mauritania","Mauritius","Morocco","Namibia","Niger","Nigeria","Rwanda","Senegal","Sierra Leone","Somalia","South Africa","South Sudan", "Sudan","Tanzania","Togo","Tunisia","Uganda","Zambia","Zimbabwe")

  ctnt <- case_when(country %in% Europe ~ "Europe",
                  country %in% Australia ~ "Australia",
                  country %in% Asia ~ "Asia",
                  country %in% North_America ~ "North_America",
                  country %in% South_America ~ "South_America",
                  country %in% Africa ~ "Africa")
  ctnt
  }
  
  df %>% 
    mutate(continent=return_continent(country))
}
```

```{r test get_continent function}
get_continent(df1, country) %>% 
  select(country, continent) %>% 
  assert(in_set("Europe","Australia","Asia","North_America","South_America","Africa", allow.na = FALSE), continent)
```

I want to divide the happiness ranks into four levels, and label them starting from A to D. Hopefully I can see some patterns here.
```{r get level for happiness level}
get_level <- function(df, x, y){

  df %>%
    mutate(happiness_level.x= case_when({{x}} < quantile({{x}}, 0.25)[[1]] ~ "A",
                                      {{x}} >= quantile({{x}}, 0.25)[[1]] & {{x}} < median({{x}}) ~ "B",
                                      {{x}} >= median({{x}}) & {{x}} < quantile({{x}}, 0.75)[[1]] ~ "C",
                                      {{x}} >= quantile({{x}}, 0.75)[[1]] ~ "D"
                             )) %>%
    mutate(happiness_level.x=as.factor(happiness_level.x)) %>%
    mutate(happiness_level.y= case_when({{y}} < quantile({{y}}, 0.25)[[1]] ~ "A",
                                      {{y}} >= quantile({{y}}, 0.25)[[1]] & {{y}} < median({{y}}) ~ "B",
                                      {{y}} >= median({{y}}) & {{y}} < quantile({{y}}, 0.75)[[1]] ~ "C",
                                      {{y}} >= quantile({{y}}, 0.75)[[1]] ~ "D"
                             )) %>%
    mutate(happiness_level.y=as.factor(happiness_level.y))
}
```

```{r test the get_level function}
get_level(df1, happiness_rank.x, happiness_rank.y) %>% 
  select(happiness_rank.x, happiness_level.x, happiness_rank.y, happiness_level.y) %>% 
  assert(in_set("A","B","C","D", allow.na = FALSE), happiness_level.x) %>% 
  assert(in_set("A","B","C","D", allow.na = FALSE), happiness_level.y)
```

I observed that the parameters we have here can be devided into two groups, personal satisfaction and social satisfaction. In the personal satisfaction, I will include family.x, health_life_expectancy.x, freedom.x, generosity.x, And for the social satisfaction, I will include the left, namely economy_gdp_per_capita.x, trust_government_corruption.x, dystopia_residual.x. 
```{r personal satisfaction function}
get_personal_satis <- function(df,a,b,c,d){
  df %>%
    mutate(personal_satis = {{a}}+{{b}}+{{c}}+{{d}})
}
#get_social_satis funciton
```

```{r test get_personal_satis}
get_personal_satis(df1, family.x, health_life_expectancy.x, freedom.x, generosity.x) %>% 
  get_social_satis(economy_gdp_per_capita.x, trust_government_corruption.x, dystopia_residual.x) %>% 
  select(country, personal_satis, social_satis) %>% 
  assert(within_bounds(lower.bound = 0, upper.bound = Inf, allow.na = FALSE), personal_satis) %>% 
  assert(within_bounds(lower.bound = 0, upper.bound = Inf, allow.na = FALSE), social_satis)
```




